---
title: "rn3-behavior-analyses"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages, include = 'false'}
library(Rmisc)
library(dplyr)
library(tidyr)
library(data.table)
library(ggplot2)
library(ggrain)
library(wesanderson)
library(gridExtra)
```

## Open datafile

Open the original csv files and combine for every session and participant
```{r open data}
path = '/Users/rosenasrawi/Documents/VU PhD/Projects/rn3 - Sequential encoding/Data/Lab data/logfiles/'

subjectIDs = c('s01', 's02', 's03', 's04', 's05', 's07', 's08', 's09', 's10', 's11', 's12', 's13', 's14', 's15', 's16', 's17', 's18', 's19', 's21', 's22', 's23', 's24', 's25', 's26', 's27')
sessions = c('a', 'b')

data = c() # Empty to start

for (sID in subjectIDs){

  for (ses in sessions){
    filename = paste('rn3_', sID, ses, '.csv', sep = "")
    sub_data = read.csv(paste(path, filename, sep = ""))
    
    numtrials = dim(sub_data)[1] # number of rows in new file
    sub_data$subjectID = rep(sID, numtrials)
    
    data = rbind(data, sub_data) # Add every session to 1 file
  }
  
}

head(data)

```

## Clean data

Clean the data by decision times

```{r clean data}
slow_trials_all = c()

for (sub in unique(data$subjectID)){
  
  mean_sub = mean(data$responseTime[which(data$subjectID == sub)])
  sd_sub = sd(data$responseTime[which(data$subjectID == sub)]) * 2.5
  
  cutoff_slow = mean_sub + sd_sub
  
  slow_trials_sub = which(data$subjectID == sub & data$responseTime > cutoff_slow)
  
  if (length(slow_trials_sub) >= 1){
    slow_trials_all = c(slow_trials_all, slow_trials_sub)
  }
  
}

slow_trials_all = as.numeric(slow_trials_all)

data$responseTimeClean = data$responseTime
data$responseTimeClean[slow_trials_all] = NaN
data$responseTimeClean[which(data$responseTime >= 5)] = NaN
data$responseTimeClean[which(data$responseTime <= 0.1)] = NaN

data$goodBadTrials = T
data$goodBadTrials[slow_trials_all] = F
data$goodBadTrials[which(data$responseTime >= 5)] = F
data$goodBadTrials[which(data$responseTime <= 0.1)] = F

```

## Conditions as factors

```{r as factors}

data$subjectID = as.factor(data$subjectID)

data$loadType = as.factor(data$loadType)
levels(data$loadType) = c("One", "Two")

data$targetMoment = as.factor(data$targetMoment)
levels(data$targetMoment) = c("Early", "Late")

data$dialType = as.factor(data$dialType)
levels(data$dialType) = c("Up", "Right")

data$targetLocation = as.factor(data$targetLocation)

data$colProbed = as.factor(data$colProbed)
levels(data$colProbed) = c("Green", "Blue", "Yellow", "Red")

data$clockwise = as.factor(data$clockwise)

```

## Median split performance 

```{r median split performance}

med.RT1.subj = tapply(data$responseTimeClean, list(data$subjectID, data$loadType, data$targetMoment, data$dialType, data$targetLocation, data$clockwise), FUN = median, na.rm=TRUE)
fastSlow = data$responseTimeClean

med.err.subj = tapply(data$difference, list(data$subjectID, data$loadType, data$targetMoment, data$dialType, data$targetLocation, data$clockwise), FUN = median, na.rm=TRUE)
precImprec = data$difference

for (sub in 1:length(levels(data$subjectID))){
  for (load in 1:length(levels(data$loadType))){
    for (tmom in 1:length(levels(data$targetMoment))){
      for (dial in 1:length(levels(data$dialType))){
        for (tloc in 1:length(levels(data$targetLocation))){
          for (hand in 1:length(levels(data$clockwise))){

            # Conditions
            this.sub = levels(data$subjectID)[sub]
            this.load = levels(data$loadType)[load]
            this.tmom = levels(data$targetMoment)[tmom]
            this.dial = levels(data$dialType)[dial]
            this.tloc = levels(data$targetLocation)[tloc]
            this.hand = levels(data$clockwise)[hand]
            
            # Fast vs slow
            this.med.RT = med.RT1.subj[sub,load,tmom,dial,tloc,hand] 
            
            fastSlow[data$subjectID == this.sub & data$loadType == this.load & data$targetMoment == this.tmom & data$dialType == this.dial & data$targetLocation == this.tloc & data$clockwise == this.hand & data$responseTimeClean > this.med.RT] = 'slow'
            fastSlow[data$subjectID == this.sub & data$loadType == this.load & data$targetMoment == this.tmom & data$dialType == this.dial & data$targetLocation == this.tloc & data$clockwise == this.hand & data$responseTimeClean < this.med.RT] = 'fast'
            fastSlow[data$subjectID == this.sub & data$loadType == this.load & data$targetMoment == this.tmom & data$dialType == this.dial & data$targetLocation == this.tloc & data$clockwise == this.hand & data$responseTimeClean == this.med.RT] = NaN
            
            # Prec vs imprec
            this.med.err = med.err.subj[sub,load,tmom,dial,tloc,hand] 

            precImprec[data$subjectID == this.sub & data$loadType == this.load & data$targetMoment == this.tmom & data$dialType == this.dial & data$targetLocation == this.tloc & data$clockwise == this.hand & data$difference < this.med.err] = 'prec'
            precImprec[data$subjectID == this.sub & data$loadType == this.load & data$targetMoment == this.tmom & data$dialType == this.dial & data$targetLocation == this.tloc & data$clockwise == this.hand & data$difference > this.med.err] = 'imprec'
            precImprec[data$subjectID == this.sub & data$loadType == this.load & data$targetMoment == this.tmom & data$dialType == this.dial & data$targetLocation == this.tloc & data$clockwise == this.hand & data$difference == this.med.err] = NaN
            
          }    
        }
      }
    }
  } 
}

fastSlow[is.nan(data$responseTimeClean)] = NaN

data$fastSlow = fastSlow
data$precImprec = precImprec

```

## T1/T2 stay/switch

```{r moment stay/switch}

# define blocks

ntrials = 32
nblocks = sum(data$subjectID == 's01')/ntrials

block = c()
for (b in 1:nblocks) {block = append(block, rep(b, ntrials))}

# define stay/switch for each sub

stay_switch = c()

for (sID in subjectIDs){
  
  sub_dat = data[data$subjectID == sID, ]
  sub_dat$block = block
  
  
  for (b in 1:nblocks){
    
    block_dat = sub_dat[block == b,]
    
    for (t in 1:ntrials){
      
      if (t == 1) {stay_switch = append(stay_switch, NA)} 
      
      else {
        if (block_dat$targetMoment[t] == block_dat$targetMoment[t-1]) {
          stay_switch = append(stay_switch, 'stay')
        } else {
          stay_switch = append(stay_switch, 'switch') }
        
      }
    }
  }
}

data$staySwitch = stay_switch

# Summarize

summary.rt.subj.load.moment.switch = aggregate(data = data, responseTimeClean ~ subjectID + loadType + targetMoment + staySwitch, mean)

summary.rt.load.moment.switch = summarySEwithin(data = summary.rt.subj.load.moment.switch,
                                                measurevar = "responseTimeClean",
                                                withinvars = c("loadType", "targetMoment", "staySwitch"),
                                                idvar = "subjectID")

summary.err.subj.load.moment.switch = aggregate(data = data, difference ~ subjectID + loadType + targetMoment + staySwitch, mean)

summary.err.load.moment.switch = summarySEwithin(data = summary.err.subj.load.moment.switch,
                                                measurevar = "difference",
                                                withinvars = c("loadType", "targetMoment", "staySwitch"),
                                                idvar = "subjectID")

```

## Save data

```{r save clean data file}
write.csv(data, '/Users/rosenasrawi/Documents/VU PhD/Projects/rn3 - Sequential encoding/Data/Processed/Behavior/logfiles_combined_rn3.csv', row.names=FALSE, quote=FALSE) 

```

## Summarise the data

### Decision times

```{r DT: load x targetmoment, upper & right}

summary.rt.subj.load.moment.dial = aggregate(data = data, 
                                             responseTimeClean ~ subjectID + dialType + loadType + targetMoment, 
                                             mean)

summary.rt.load.moment.dial = summarySEwithin(data = summary.rt.subj.load.moment.dial,
                                              measurevar = "responseTimeClean",
                                              withinvars = c("dialType", "loadType", "targetMoment"),
                                              idvar = "subjectID")

```

### Errors

```{r Err: load x targetmoment, upper & right}

summary.err.subj.load.moment.dial = aggregate(data = data, 
                                              difference ~ subjectID + dialType + loadType + targetMoment, 
                                              mean)

summary.err.load.moment.dial = summarySEwithin(data = summary.err.subj.load.moment.dial,
                                               measurevar = "difference",
                                               withinvars = c("dialType", "loadType", "targetMoment"),
                                               idvar = "subjectID")

```

## Plot the data

### Plot settings
```{r plot settings}

text.theme = theme(plot.title = element_text(size = 15, 
                                             hjust = 0.5, 
                                             lineheight = 1.2,
                                             family = "Helvetica Neue", 
                                             face = "bold"),
                   axis.title.x = element_text(size = 14,
                                               family = "Helvetica Neue",
                                               face = "bold"),
                   axis.title.y = element_text(size = 14,
                                               family = "Helvetica Neue",
                                               face = "bold"),
                   axis.text.x = element_text(size = 12,
                                              family = "Helvetica Neue"),
                   axis.text.y = element_text(size = 12,
                                              family = "Helvetica Neue"))


legend.theme = theme(legend.position = "bottom",
                     legend.title = element_text(size = 11,
                                                 family = "Helvetica Neue",
                                                 face = "bold"))

legend.none = theme(legend.position = "none")

color_0 = "#f58b57"
color_1 = "#8C45AC" # purple
color_2 = "#D0A1E6" # lilac 
color_3 = "#50AC7B" # green
color_4 = "#B1E6C9" # light green
 
color_5 = "#FFFF99"
color_6 = "#FFD700"
color_7 = "#FFA500"

```

### Decision times

```{r plot DT avr}

ggplot(summary.rt.load.moment.dial, aes(x = loadType, y = responseTimeClean, 
                                        col = interaction(loadType, targetMoment), 
                                        fill = interaction(loadType, targetMoment), 
                                        group = targetMoment)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.7), color = "black", 
           width = 0.6, size = 0.4) +
  geom_errorbar(aes(ymin = responseTimeClean - se, ymax = responseTimeClean + se), 
                width = 0.2, position = position_dodge(0.7), size = 0.5, color = "black") +
  scale_fill_manual(values = c(color_1, color_2, color_3, color_4),
                    breaks = c("One.Early", "One.Late", "Two.Early", "Two.Late"),
                    name = "Target Moment",
                    labels = c("Early", "Late", "Early", "Late")) +
  facet_grid(~dialType, scales = "free_x") +
  labs(x = "Memory Load", y = "Decision Time (s)") +
  coord_cartesian(ylim = c(0.1, 0.9)) +
  theme_classic() +
  theme(
    legend.position = "bottom",
    legend.title = element_text(face = "bold"),
    legend.text = element_text(size = 10),
    axis.text.x = element_text(size = 10, color = "black"),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.title.x = element_text(size = 12, color = "black", face = "bold"),
    axis.title.y = element_text(size = 12, color = "black", face = "bold"),
    strip.text = element_text(size = 12, color = "black", face = "bold")
  )




```

### Errors
```{r plot err avr}

ggplot(summary.err.load.moment.dial, aes(x = loadType, y = difference, 
                                        col = interaction(loadType, targetMoment), 
                                        fill = interaction(loadType, targetMoment), 
                                        group = targetMoment)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.7), color = "black", 
           width = 0.6, size = 0.4) +
  geom_errorbar(aes(ymin = difference - se, ymax = difference + se), 
                width = 0.2, position = position_dodge(0.7), size = 0.5, color = "black") +
  scale_fill_manual(values = c(color_1, color_2, color_3, color_4),
                    breaks = c("One.Early", "One.Late", "Two.Early", "Two.Late"),
                    name = "Target Moment",
                    labels = c("Early", "Late", "Early", "Late")) +
  facet_grid(~dialType, scales = "free_x") +
  labs(x = "Memory Load", y = "Absolute error (deg)") +
  coord_cartesian(ylim = c(3, 22)) +
  theme_classic() +
  theme(
    legend.position = "bottom",
    legend.title = element_text(face = "bold"),
    legend.text = element_text(size = 10),
    axis.text.x = element_text(size = 10, color = "black"),
    axis.text.y = element_text(size = 10, color = "black"),
    axis.title.x = element_text(size = 12, color = "black", face = "bold"),
    axis.title.y = element_text(size = 12, color = "black", face = "bold"),
    strip.text = element_text(size = 12, color = "black", face = "bold")
  )

```

### Raincloud main effects

```{r DT main effect}

rt.sub.load = data %>% 
  group_by(subjectID, loadType) %>% 
  summarise(loadRT = mean(responseTimeClean, na.rm = TRUE)) %>% 
  pivot_wider(names_from = loadType, values_from = loadRT) %>% 
  transmute(Effect = Two - One)

rt.sub.dial = data %>% 
  group_by(subjectID, dialType) %>% 
  summarise(dialRT=mean(responseTimeClean, na.rm=TRUE)) %>% 
  pivot_wider(names_from=dialType,values_from=dialRT) %>% 
  transmute(Effect = Right - Up)

rt.sub.momt = data %>% 
  group_by(subjectID, targetMoment) %>% 
  summarise(momentRT=mean(responseTimeClean, na.rm=TRUE)) %>% 
  pivot_wider(names_from=targetMoment,values_from=momentRT) %>% 
  transmute(Effect = Early - Late)

rt.effects = bind_rows(
  list(Load = rt.sub.load, Dial = rt.sub.dial, Moment = rt.sub.momt),
  .id = 'effectType')

rt.effects$effectType = factor(rt.effects$effectType, levels=c("Load", "Dial", "Moment"))
rt.effects$effectType = factor(rt.effects$effectType, levels = rev(levels(rt.effects$effectType)))

```

```{r err main effect}

err.sub.load = data %>% 
  group_by(subjectID, loadType) %>% 
  summarise(loadRT = mean(difference, na.rm = TRUE)) %>% 
  pivot_wider(names_from = loadType, values_from = loadRT) %>% 
  transmute(Effect = Two - One)

err.sub.dial = data %>% 
  group_by(subjectID, dialType) %>% 
  summarise(dialRT=mean(difference, na.rm=TRUE)) %>% 
  pivot_wider(names_from=dialType,values_from=dialRT) %>% 
  transmute(Effect = Right - Up)

err.sub.momt = data %>% 
  group_by(subjectID, targetMoment) %>% 
  summarise(momentRT=mean(difference, na.rm=TRUE)) %>% 
  pivot_wider(names_from=targetMoment,values_from=momentRT) %>% 
  transmute(Effect = Early - Late)

err.effects = bind_rows(
  list(Load = err.sub.load, Dial = err.sub.dial, Moment = err.sub.momt),
  .id = 'effectType')

err.effects$effectType = factor(err.effects$effectType, levels=c("Load", "Dial", "Moment"))
err.effects$effectType <- factor(err.effects$effectType, levels = rev(levels(err.effects$effectType)))

```

``` {r rain DT main effects}

ggplot(rt.effects, aes(x = effectType, y = Effect, fill = effectType))+ 
  
  geom_rain(point.args = rlang::list2(color = "grey", size = 1.5),
            violin.args = list(alpha = 1, size = 1, linewidth = 0.7, width = 1),
            boxplot.args = list(alpha = 1, linewidth = 0.7, width = .075)) +
  
  geom_hline(yintercept = 0, linetype = 2) +

  scale_fill_manual(values = c(color_5, color_6, color_7)) +

  scale_y_continuous("Decision time difference (s)") +
  scale_x_discrete("Main effects") +

  theme_classic() +
  text.theme +
  legend.none +
  coord_flip()

```

``` {r rain DT main effects flipped}

ggplot(rt.effects, aes(x = effectType, y = Effect, fill = effectType)) +
  
  geom_violin(alpha = 1, size = 0.75, width = 0.8, trim = FALSE) +
  geom_boxplot(alpha = 1, width = 0.1, outlier.shape = NA) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
  
  scale_fill_manual(values = c(color_5, color_6, color_7)) +
  scale_y_continuous("Decision time difference (s)") +
  scale_x_discrete("Main effects") +

  theme_classic() +
  text.theme +
  legend.none +
  coord_flip()

```

``` {r rain err main effects}

ggplot(err.effects, aes(x = effectType, y = Effect, fill = effectType))+ 
  
  geom_rain(point.args = rlang::list2(color = "grey", size = 1.5),
            violin.args = list(alpha = 1, size = 1, linewidth = 0.7, width = 1),
            boxplot.args = list(alpha = 1, linewidth = 0.7, width = .075)) +
  
  geom_hline(yintercept = 0, linetype = 2) +

  scale_fill_manual(values = c(color_5, color_6, color_7)) +

  scale_y_continuous("Error difference (deg)") +
  scale_x_discrete("Main effects") +

  theme_classic() +
  text.theme +
  legend.none +
  coord_flip()

```

```{r rain err main effects flipped }

ggplot(err.effects, aes(x = effectType, y = Effect, fill = effectType)) +
  
  geom_violin(alpha = 1, size = 0.75, width = 0.8, trim = FALSE) +
  geom_boxplot(alpha = 1, width = 0.1, outlier.shape = NA) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
  
  scale_fill_manual(values = c(color_5, color_6, color_7)) +
  scale_y_continuous("Error difference (deg)") +
  scale_x_discrete("Main effects") +

  theme_classic() +
  text.theme +
  legend.none +
  coord_flip()

```


### Precision per angle

```{r plot prec per angle}

# Change target ori to [-90 , 90]
data$askDegree90 = data$askDegree
data$askDegree90[data$askDegree >= 90] = data$askDegree[data$askDegree >= 90] - 180

# Change report ori to [-90 , 90]
data$repDegree90 = data$repDegree
data$repDegree90[data$repDegree >= 90] = data$repDegree[data$repDegree >= 90] - 180

# Bin data
tilt_bins = rbind(c(seq(-85,-25,20), seq(5,65,20)), c(seq(-65,-5,20), seq(25,85,20)))

nbins = dim(tilt_bins)[2]
data$askDegree90Steps = data$askDegree90
bin_titles = c()

for (b in 1:nbins) {
  this_bin = tilt_bins[,b]
  data_bin = data$askDegree90 >= this_bin[1] & data$askDegree90 <= this_bin[2]
  data$TargetOri90Steps[data_bin] = b
  bin_titles[b] = paste(as.character(this_bin[1]), "to", as.character(this_bin[2]))
}

colfunc <- colorRampPalette(c("blue3", "white"))
blue_grad = colfunc(round(nbins/2)+2)
blue_grad = blue_grad[-c(round(nbins/2)+2, round(nbins/2)+1)]

colfunc <- colorRampPalette(c("white", "red3"))
red_grad = colfunc(nbins-round(nbins/2)+2)
red_grad = red_grad[-c(1,2)]

blue_red = c(blue_grad, red_grad)
```

```{r plot prec per angle, load}

precision_density = data.frame(Target = as.factor(data$TargetOri90Steps), Report = data$repDegree90)
precision_density$loadType = data$loadType

ggplot(precision_density, aes(x=Report, color=Target)) +
  
  geom_density(show.legend = FALSE) + 
  stat_density(geom = "line", position = "identity", size = 0.8) + 
  scale_color_manual(labels = bin_titles, values = blue_red)+
  scale_x_continuous("Reported orientation") +
  scale_y_continuous("Response density") +
  
  facet_grid(~loadType, scales = 'free_x')+
  
  theme_bw() +
  text.theme +
  legend.theme +
  guides(colour = guide_legend(override.aes=list(size=0.5)))

```
```{r plot prec per angle, target moment}

precision_density$targetMoment = data$targetMoment

ggplot(precision_density, aes(x=Report, color=Target)) +
  
  geom_density(show.legend = FALSE) + 
  stat_density(geom = "line", position = "identity", size = 0.8) + 
  scale_color_manual(labels = bin_titles, values = blue_red)+
  scale_x_continuous("Reported orientation") +
  scale_y_continuous("Response density") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +

  facet_wrap(~loadType + targetMoment, scales = 'free_x', nrow = 2)+
  
  theme_classic() +
  theme(legend.key.size = unit(0.5, "lines")) +
  labs(color = "Target") +
  guides(color = guide_legend(override.aes = list(size = 1))) +
  ggtitle("Density Plot of Reported Orientation by Target and Load Type")

```

# ANOVA: load x moment x dial

### Absolute error
```{r stat error}
anov_Err <- aov(difference ~ loadType * targetMoment * dialType, data = summary.err.subj.load.moment.dial)
summary(anov_Err)
```

### Decision time
```{r stat dt}
anov_RT <- aov(responseTimeClean ~ loadType * targetMoment * dialType, data = summary.rt.subj.load.moment.dial)
summary(anov_RT)
```
