---

title: "rn3_encoding_barplot_timeavg_TFR"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r packages, include = 'false'}
library(Rmisc)
library(dplyr)
library(data.table)
library(ggplot2)
library(wesanderson)
library(gridExtra)
```
# Encoding cvsi

## Open datafile

Open the original csv files and combine for every session and participant
```{r open data}
path = '/Users/rosenasrawi/Documents/VU PhD/Projects/rn3 - Sequential encoding/Data/Processed/EEG/Locked encoding/timecourse average/'

filename = 'mean_cvsi_motor_beta_postenc.csv'
headername = 'header_mean_cvsi_motor_beta_postenc.csv'

data = read.csv(paste(path, filename, sep = ""))
names(data) = names(read.csv(paste(path, headername, sep = "")))

subjects = 1:25

for (sub in 1:length(subjects)) {
  sub
  if (sub < 10) {
    subjects[sub] = paste('s0', as.character(sub), sep = "")
  } else {
    subjects[sub] = paste('s', as.character(sub), sep = "")
  }
}
```

## Summarise the data

```{r timecourse average: load x moment}

summary.tcravg.subj.load.moment = data.frame(row.names = 1:(length(subjects)*length(data)))

summary.tcravg.subj.load.moment$subjectID      = rep(subjects, length(data))
summary.tcravg.subj.load.moment$loadType       = c(rep('load one-T1', 2*length(subjects)), 
                                                            rep('load one-T2', 2*length(subjects)), 
                                                            rep('load two',  2*length(subjects)))
summary.tcravg.subj.load.moment$momentType     = rep(c(rep('postenc-T1', length(subjects)), rep('postenc-T2', length(subjects))),3)
summary.tcravg.subj.load.moment$timecourseAvg  = c(data$load1.T1.T1, data$load1.T1.T2, 
                                                            data$load1.T2.T1, data$load1.T2.T2, 
                                                            data$load2.T1, data$load2.T2)

summary.tcravg.load.moment = summarySE(data = summary.tcravg.subj.load.moment,
                                              measurevar = "timecourseAvg",
                                              groupvars = c("loadType", "momentType"))

summary.tcravg.load.moment

```

## Plot the data

### Plot settings
```{r plot settings}

text.theme = theme(plot.title = element_text(size = 15, 
                                             hjust = 0.5, 
                                             lineheight = 1.2,
                                             family = "Helvetica Neue", 
                                             face = "bold"),
                   axis.title.x = element_text(size = 14,
                                               family = "Helvetica Neue",
                                               face = "bold"),
                   axis.title.y = element_text(size = 14,
                                               family = "Helvetica Neue",
                                               face = "bold"),
                   axis.text.x = element_text(size = 12,
                                              family = "Helvetica Neue"),
                   axis.text.y = element_text(size = 12,
                                              family = "Helvetica Neue"))


legend.theme = theme(legend.position = "bottom",
                     legend.title = element_text(size = 11,
                                                 family = "Helvetica Neue",
                                                 face = "bold"))

legend.none = theme(legend.position = "none")

color_1 = "#50b17b" # green
color_2 = "#a7d8bc" # lightgreen

```

### Timecourse average: load x moment
```{r plot DT avr}

ggplot(summary.tcravg.load.moment, 
       aes(x = loadType, y = timecourseAvg, 
           col = interaction(loadType,momentType), 
           fill = interaction(loadType,momentType), 
           group = momentType)) +
  
  geom_bar(stat = "identity", position = position_dodge(width = 1), 
           color = "black", width = 0.5, size = 0.4) +
  
  geom_errorbar(aes(ymin = timecourseAvg-se, ymax = timecourseAvg+se), width = 0.1, 
                position = position_dodge(1), size = 0.5, color = "black") +  
  
  scale_fill_manual(values = rep(c(color_1, color_2),3))+
  
  facet_grid(~loadType, scales = 'free_x')+
  scale_y_continuous("Average motor beta post-encoding") +
  scale_x_discrete("Memory load") +

  coord_cartesian(ylim = c(-4,4)) +

  theme_bw() +
  text.theme +
  legend.none

```
# Encoding cvsi performance

## Open datafile

Open the original csv files and combine for every session and participant
```{r open data perf}
path = '/Users/rosenasrawi/Documents/VU PhD/Projects/rn3 - Sequential encoding/Data/Processed/EEG/Locked encoding/timecourse average/'

filename = 'mean_cvsi_motor_beta_perf_postenc.csv'
headername = 'header_mean_cvsi_motor_beta_perf_postenc.csv'

data = read.csv(paste(path, filename, sep = ""))
names(data) = names(read.csv(paste(path, headername, sep = "")))

subjects = 1:25

for (sub in 1:length(subjects)) {
  sub
  if (sub < 10) {
    subjects[sub] = paste('s0', as.character(sub), sep = "")
  } else {
    subjects[sub] = paste('s', as.character(sub), sep = "")
  }
}
```

## Summarise the data

```{r timecourse average load 2: moment x perf}

summary.tcravg.subj.moment.perf = data.frame(row.names = 1:(length(subjects)*length(data)))

summary.tcravg.subj.moment.perf$subjectID      = rep(subjects, length(data))

summary.tcravg.subj.moment.perf$momentType     = c(rep('load-two-T1', 2*length(subjects)), rep('load-two-T2', 2*length(subjects)))

summary.tcravg.subj.moment.perf$fastSlow       = rep(c(rep('fast', length(subjects)), rep('slow', length(subjects))),2)

summary.tcravg.subj.moment.perf$timecourseAvg  = c(data$load2.T1.fast, data$load2.T1.slow, data$load2.T2.fast, data$load2.T2.slow)


summary.tcravg.moment.perf = summarySE(data = summary.tcravg.subj.moment.perf,
                                              measurevar = "timecourseAvg",
                                              groupvars = c("momentType", "fastSlow"))

summary.tcravg.moment.perf

```

### Timecourse average: moment x perf
```{r plot DT avr perf}

ggplot(summary.tcravg.moment.perf, 
       aes(x = momentType, y = timecourseAvg, 
           col = interaction(momentType,fastSlow), 
           fill = interaction(momentType,fastSlow), 
           group = fastSlow)) +
  
  geom_bar(stat = "identity", position = position_dodge(width = 1), 
           color = "black", width = 0.5, size = 0.4) +
  
  geom_errorbar(aes(ymin = timecourseAvg-se, ymax = timecourseAvg+se), width = 0.1, 
                position = position_dodge(1), size = 0.5, color = "black") +  
  
  scale_fill_manual(values = c(color_1, color_1, color_2, color_2))+
  
  facet_grid(~momentType, scales = 'free_x')+
  scale_y_continuous("Average motor beta post-encoding") +
  scale_x_discrete("Memory load") +

  coord_cartesian(ylim = c(-5,2)) +

  theme_bw() +
  text.theme +
  legend.none

```
### ANOVA: moment x perf
```{r stat moment x perf}
anov_RT <- aov(timecourseAvg ~ momentType * fastSlow, data = summary.tcravg.subj.moment.perf)
summary(anov_RT)
TukeyHSD(anov_RT)

```